Paper_notes

### 2017-10-16 Paper_notes.Rmd
Add files via upload
paper 20171016

>>>>

### Altman & Krzywinski, 2014

Altman, N., Krzywinski M. “Points of Significance: Sources of Variation.” Nature Methods 12, no. 1 (December 30, 2014): 5–6. doi:10.1038/nmeth.3224

All experiments are exposed to different sources of variability. While some sources affect the internal validity of the experiment, others affect external validity. It is essential to identify the sources of variability, to control or measure them, to have more precise and unbiased estimates. 
Biological variability, for example, phenotype and genotype data, can be controlled by fixing the levels of these variables and randomizing to treatments. 
On another hand, replication increases the precision of the estimates and allows to measure the variability from different sources. Additionally, replications in top layers have more impact on the precision than in later layers. 
Finally, blocking can control both internal and external variability, for example using siblings controls external variability and blocking by a technician controls internal variability. With this reduction in variability, blocking increases power in tests for comparisons between treatments.
